### 2012-06-07 FFI-Simulator/ffi-simulator.tex
...

>>>>

\newpage

\section{Ideas for paper}

\begin{itemize}
\item With effects such as layover, shadows, limited resolution (detail retention capability), and complex object and surface shapes, computing the actual scenario based on the sonar image is hard.
\item Better to perform fast, recursive simulations instead?
\item Adaptive images in a video makes it much easier to understand what is going on. Need much better erfora
\item Litits: massive storage, fixed templates, amplitude/noise sensitive
\item Alternatives: Pattern recognition (hard to extract decent features, selection, fixed templates) and model-based (massive computational requirements)
\item Why models? Hard to get accurate models from limted amount dat, targets not always availagme, variations in target/terrain.
\item CAD models. Sufficient complexity? Materials? Transparency, characterisation, multilauers.
\item Accuracy vs. comp. speed.
\end{itemize}
